\LARGE \bf Planning with Attitude

### 2020-10-14 paper/main.tex

    \subsection{Methodology}
% \todo{Let's keep our notation and language consistent for body vs. inertial frames. I propose ``body'' (B) and ``inertial'' or ``world'' (W), which is the standard in robotics.}
    Given a set of known vectors in the world frame, $\inframe{W}{w_i}$, and measurements of these vectors in the body frame, $\inframe{B}{v_i}$, we seek the
    rotation from the body to the world frame $\toframe{W}{B}{A(q)}$ that solves the following optimization problem, \todo{Kevin: Don't use $L$ here because it conflicts with \eqref{eq:Lmult}:}
    \begin{mini*}
        {q}{ L(q) }{}{}
        \addConstraint { q\in \Q,}
    \end{mini*}
    where Wahba's loss function $L(q)$ is,
    \begin{equation} \label{eq:wahba_loss}
        L(q) = \sum_i \norm{\inframe{W}{w_i} - A(q) \,\, \inframe{B}{v_i} }_2^2 
           = \norm{r(q)}_2^2 ,
    \end{equation} 
    and $r(q)$ is the residual vector.

    The Jacobian of $r(q)$ can be found using \eqref{eq:quat_jacobian} and \eqref{eq:quaternion_rotation}: \todo{Kevin: fix the second line of this equation:}
    \begin{equation} \label{eq:newton_foc}
        \begin{aligned}
            \nabla r(q) &= \pdv{r}{q} G(q) \\
              &= \left( \sum_i -2 H^T R(q)^T R({}^B \hat{v}_i) \right).
        \end{aligned}
    \end{equation}
    Given a guess solution, $q_k$, The standard Gauss-Newton method can then be used to compute a three-parameter update $\phi_k$ via the Moore-Penrose psuedoinverse:
    \begin{equation}
    	\phi_k = ({\nabla r}^T {\nabla r})^{-1} {\nabla r}^T r(q_k).
    \end{equation}
	The update is then applied using the composition for the group:
	\begin{equation}
		\q_{k+1} = \q_k \otimes \varphi(\phi_k)
	\end{equation}.
	This ``multiplicative'' Gauss-Newton method is summarized in Algorithm \ref{alg:mgn}.

>>>>

    \subsection{Methodology}
% \todo{Let's keep our notation and language consistent for body vs. inertial frames. I propose ``body'' (B) and ``inertial'' or ``world'' (W), which is the standard in robotics.}
    Given a set of known vectors in the world frame, $\inframe{W}{w_i}$, and measurements of these vectors in the body frame, $\inframe{B}{v_i}$, we seek the
    rotation from the body to the world frame $\toframe{W}{B}{A(q)}$ that solves the following optimization problem,
    \begin{mini*}
        {q}{ W(q) }{}{}
        \addConstraint { q\in \Q,}
    \end{mini*}
    where Wahba's loss function $W(q)$ is,
    \begin{equation} \label{eq:wahba_loss}
        W(q) = \sum_i \norm{\inframe{W}{w_i} - A(q) \,\, \inframe{B}{v_i} }_2^2 
           = \norm{r(q)}_2^2 ,
    \end{equation} 
    and $r(q)$ is the residual vector.

    The Jacobian of $r(q)$ can be found using \eqref{eq:quat_gradient}:
    \begin{align} \label{eq:newton_foc}
            \nabla r(q) &= \pdv{r}{q} G(q) \\
              &= \left( \sum_i -2 H^T R(q)^T R({}^B \hat{v}_i) G(q)\right).
    \end{align}
    Given a guess solution, $q_k$, The standard Gauss-Newton method can then be used to compute a three-parameter update, $\phi_k$ via the Moore-Penrose psuedoinverse:

    \begin{equation}
    	\phi_k = ({\nabla r}^T {\nabla r})^{-1} {\nabla r}^T r(q_k).
    \end{equation}
	The update is then applied using the composition for the group:
	\begin{equation}
		\q_{k+1} = \q_k \otimes \varphi(\phi_k)
	\end{equation}.
	This ``multiplicative'' Gauss-Newton method is summarized in Algorithm \ref{alg:mgn}.
